Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
fix space
fixing citation linking errors

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \ref{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
%(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
(See ~\cite{fifield2015blocking} for additional details.)\\
\end{itemize}

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Google search for the population of Zimbabwe. 
\item On YouTube, find a video playing Bach's ``Ode to Joy.''
\item Find the Amazon best-sellers in ``Movies \& TV.''
\item On Yahoo, find the exchange rate of Dollars to Euros.
\item Find the Wikipedia ``History'' portal's featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Times Square to Carnegie Hall.
\end{itemize}

>>>>

There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management. Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
Internet censorship is shown to be pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
%(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
``meek-amazon,'' ``meek-azure,'' and ``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
(See ~\cite{fifield2015blocking} for additional details.)\\
\end{itemize}

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Google search for the population of Zimbabwe. 
\item On YouTube, find a video playing Bach's ``Ode to Joy.''
\item Find the Amazon best-sellers in ``Movies \& TV.''
\item On Yahoo, find the exchange rate of Dollars to Euros.
\item Find the Wikipedia ``History'' portal's featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Times Square to Carnegie Hall.\\
\end{itemize}

\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} blah blah}
